Case study validations of automatic bullet matching

### 2018-10-16 index.Rmd
messing about with validation cases

The algorithm in \citet{aoas} is trained on scans from Hamby sets 252 and 173 made available through \citet{nist}. Set 173 was originally published as Hamby set 44. This mislabelling has been correct now. The scans used to train the model were taken at 20 fold magnification for a resolution of 1.5625 microns per pixel. \hh{While magnification is generally of interest in microscopy, {\it resolution} -- usually measured in microns per pixel -- is of more interest for 3D topographic measurements, as it determines the operative level of available data.}

@@

Scans of all land engraved areas were taken on a Sensofar Confocal Light microscope at 20x magnification resulting in a resolution of 0.645 microns per pixel. If not indicated otherwise, scans were taken at the Roy J Carver high resolution microscopy lab at Iowa State University.

>>>>

The algorithm in \citet{aoas} is trained on scans from Hamby sets 252 and 173 made available through \citet{nist}. Set 173 was originally published as Hamby set 44. This mislabelling has been correct now.

@@

The scans used to train the model were taken at 20 fold magnification for a resolution of 1.5625 microns per pixel. While magnification is generally of interest in microscopy, {\it resolution} -- usually measured in microns per pixel -- is of more interest for 3D topographic measurements, as it determines the operative level of available data.

Scans of all land engraved areas for the validation data were taken on a Sensofar Confocal Light microscope at 20x magnification resulting in a resolution of 0.645 microns per pixel. If not indicated otherwise, scans were taken at the Roy J Carver high resolution microscopy lab at Iowa State University.
